An Overview of Distributed Version Control Systems

### 2010-07-04 laarsample.tex
Quitados un par de you

Then the developers can share their changes by pushing them into someone else's repository or by pulling changes from them.
Therefore, if you work distributed, merges would happen on a regular basis and they should be as fast and easy as possible, providing developers with a whole new set of tools that relieve them almost completely from having to code according to the rules required to work with a centralized CVS like system.

@@

\emph{Pull:} 
Pull is the opposite action of push and it is the combination of two other commands, ``fetch'' and ``merge''. The fetch command takes the changes from a peer's repository and copies them to the local repository. After that, the merge process combines the changes you've just downloaded with the ones on your local repository. You can do those two actions separatedly or altogether by using the ``pull'' command.

>>>>

Then the developers can share their changes by pushing them into someone else's repository or by pulling changes from them.
Therefore, if the work environment is distributed, merges would happen on a regular basis and they should be as fast and easy as possible, providing developers with a whole new set of tools that relieve them almost completely from having to code according to the rules required to work with a centralized CVS like system.

@@

\emph{Pull:} 
Pull is the opposite action of push and it is the combination of two other commands, ``fetch'' and ``merge''. The fetch command takes the changes from a peer's repository and copies them to the local repository. After that, the merge process combines the changes that have been just pulled with the ones on the local repository. Those two actions can be executed separatedly or altogether by using the ``pull'' command.
